The effects of varying depth in cosmic shear surveys

### 2019-10-02 paperdraft.tex
added some acknowledgements

\begin{acknowledgements}
I feel like something should be put here.
\end{acknowledgements}

>>>>

\begin{acknowledgements}
The KV450 results in this paper are based on data products from observations
made with ESO Telescopes at the La Silla Paranal Observatory under programme
IDs 177.A-3016, 177.A-3017 and 177.A-3018, and on data products produced by
Target/OmegaCEN, INAF-OACN, INAF-OAPD and the KiDS production team,
on behalf of the KiDS consortium.
\\
This research has made use of NASA's Astrophysics Data System and adstex (\url{https://github.com/yymao/adstex}).
\end{acknowledgements}
